### 2016-07-06 filters.tex
adding a new heading/placeholder for results about the privacy of certain BF schemes

>>>>

\heading{Achieving FP-security and privacy.}
\tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the min-entropy of $\distr{U}{n}$.}
\tsnote{We should prove privacy for the bigram/PRF-based double-hashing construction that Neidermayer et al.\ attacks. I'm pretty sure the attack is in the public-BB setting, and the provable security bound is considerably worse than the min-entropy because of the way the representation is made.  (Essentially, the Hamming weight of the representation is a good estimate of the length of the longest surname in filter.)  Note that their attack would allow one to recover \emph{every} name, not just one.}
\tsnote{Prove that the basic BF, in the ROM, is private.  This also shows that the basic BF with $h_j(x)=F_K(\langle j,x \rangle)$ is private.  I believe this also shows that the bigram approach examined by Neidermayer et al.\ is secure when the hash functions are the $h_j(x)$ just described. }
\tsnote{Prove privacy of other suggestions, such as the record-level BF from Durham et al.?}

### 2016-07-06 intro.tex
adding a new heading/placeholder for results about the privacy of certain BF schemes

There are applications in which the proposed Bloom filter instantiations do
use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot
g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in
the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
This particular ``encrypted Bloom filter'' instantiation was
suggested for use in efficient linking of records across separate
medical record databases~\cite{xxx}.  (It was subsequently shown not
to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of
frequency analysis recovered the last names of patients given access
only to the Bloom filter array.\tsnote{This shows that
false-positive security and privacy (whatever it is) are orthogonal,
since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})
In any case, it is clear that the NY definition does not capture the
most widely used applications of Bloom filters, e.g. CDN summary
caches, P2P network routing algorithms, etc. \tsnote{Could also
point out that their positive results use constructions that have
secret keys, and these are unlikely to be of any use in major
applications like CDNs or P2P networks.  But maybe the horse is
sufficiently beaten by now...}

>>>>

There are applications in which the proposed Bloom filter instantiations do
use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot
g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in
the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
This particular ``encrypted Bloom filter'' instantiation was
suggested for use in efficient linking of records across separate
medical record databases~\cite{xxx}.  (It was subsequently shown not
to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of
frequency analysis recovered the last names of patients given access
only to the Bloom filter array.)
%\tsnote{This shows that false-positive security and privacy (whatever it is) are orthogonal,
%since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})
In any case, it is clear that the NY definition does not capture the
most widely used applications of Bloom filters, e.g. CDN summary
caches, P2P network routing algorithms, etc. \tsnote{Could also
point out that their positive results use constructions that have
secret keys, and these are unlikely to be of any use in major
applications like CDNs or P2P networks.  But maybe the horse is
sufficiently beaten by now...}
